
\newcommand\AQIPittToday{49}
\newcommand\AQIPittTom{60}
\newcommand\AQILCToday{46}
\newcommand\AQILCTom{49}
\newcommand\AQIPittTodayCate{Good}
\newcommand\AQIPittTomCate{Moderate}
\newcommand\AQILCTodayCate{Good}
\newcommand\AQILCTomCate{Good}
\newcommand\AQIpitttodaypolutant{Ozone}
\newcommand\AQIpitttomorrowpolutant{Ozone}
\newcommand\AQILCtodaypolutant{PM 2.5}
\newcommand\AQILCtomorrowpolutant{PM 2.5}
\newcommand\Discriptions{Mostly sunny Saturday with a seasonably warm afternoon as a large area of high pressure builds in from the Midwest. PM2.5 will be highest during the morning, then increasing mixing will bring these levels down to the good range for an overall average. Ozone will climb close to the moderate range with the mostly sunny sky. *** Sunday's forecast: Sunday will bring sunshine and a few clouds. PM2.5 will again be highest during the morning, but increasing mixing late in the morning and afternoon will result in upper good concentrations. Ozone levels might go low moderate with the still strong sunshine. *** Monday's forecast: Monday brings times of clouds and sunshine and slightly more humid air, with scattered thunderstorms possible. Both PM2.5 and ozone will average in the upper good to lower moderate range.}
\newcommand\ADIone{Poor - 11}
\newcommand\ADItwo{Very Poor - 2}
\newcommand\ADIthree{Generally Good - 58}
\newcommand\ADIfour{Good - 66}
\newcommand\ADIfive{Very Poor - 2}
\newcommand\ADIsix{Very Poor - 1}
\newcommand\SISone{Moderate}
\newcommand\SIStwo{--}
\newcommand\SISthree{--}
\newcommand\SISfour{--}
\newcommand\SISfive{None}
\newcommand\SISsix{--}
\newcommand\Windone{W - 6}
\newcommand\Windtwo{W - 6}
\newcommand\Windthree{SW - 5}
\newcommand\Windfour{S - 5}
\newcommand\Windfive{SE - 3}
\newcommand\Windsix{S - 6}
\newcommand\Temp{3 °C}
\newcommand\Depth{247 m}
\newcommand\Time{--}
\newcommand\Scale{Moderate}
\newcommand\Inversion{No upper inversion starting below ~1000 m is reported}
\newcommand\Title{Air Quality Forecast and Dispersion Outlook \\of Allegheny County, Pennsylvania for 2022-07-30}
\newcommand\AQIPittTodayColor{6AFE19}
\newcommand\AQIPittTomColor{FFF421}
\newcommand\AQILCTodayColor{6AFE19}
\newcommand\AQILCTomColor{6AFE19}
\newcommand\AQIDateToday{07/30/2022}
\newcommand\AQIDateTom{07/31/2022}
\newcommand\AQIWeekToday{Saturday}
\newcommand\AQIWeekTom{Sunday}
\newcommand\inversionmode{observation}
