
\newcommand\AQIPittToday{46}
\newcommand\AQIPittTom{62}
\newcommand\AQILCToday{48}
\newcommand\AQILCTom{52}
\newcommand\AQIPittTodayCate{Good}
\newcommand\AQIPittTomCate{Moderate}
\newcommand\AQILCTodayCate{Good}
\newcommand\AQILCTomCate{Moderate}
\newcommand\AQIpitttodaypolutant{PM 2.5}
\newcommand\AQIpitttomorrowpolutant{Ozone}
\newcommand\AQILCtodaypolutant{PM 2.5}
\newcommand\AQILCtomorrowpolutant{PM 2.5}
\newcommand\Discriptions{Periods of clouds and sunshine Saturday. A weakening upper level low nearby will result in the development of showers and a thunderstorm, mainly during the afternoon and evening. PM2.5 will again be highest in the morning, but a south to southeast breeze will maintain overall daily average in the upper good range. Ozone will also remain in the good range with the cloud cover and potential rainfall. *** Sunday's forecast: Times of clouds and sunshine Sunday, and there canstill be a morning shower in parts of the area. The increase in sunshine will cause ozone to go into the moderate range, and while PM2.5 may be moderate for a time Sunday morning, better afternoon dispersion allows concentrations of this pollutant to decrease during the afternoon. *** Monday's forecast: Not as warm Monday as showers and thunderstorms will accompany the passage of a cold front. Air quality will return to the good range with clouds and cooler air.}
\newcommand\ADIone{Fair - 25}
\newcommand\ADItwo{Generally Good - 45}
\newcommand\ADIthree{Very Poor - 3}
\newcommand\ADIfour{Very Poor - 2}
\newcommand\ADIfive{Generally Poor - 15}
\newcommand\ADIsix{Good - 69}
\newcommand\SISone{None}
\newcommand\SIStwo{--}
\newcommand\SISthree{--}
\newcommand\SISfour{--}
\newcommand\SISfive{None}
\newcommand\SISsix{--}
\newcommand\Windone{SE - 7}
\newcommand\Windtwo{S - 5}
\newcommand\Windthree{S - 2}
\newcommand\Windfour{S - 2}
\newcommand\Windfive{SW - 5}
\newcommand\Windsix{W - 6}
\newcommand\Temp{0 °C}
\newcommand\Depth{0 m}
\newcommand\Time{--}
\newcommand\Scale{None}
\newcommand\Inversion{Yes, an upper inversion starting below ~1000 m is reported}
\newcommand\Title{Air Quality Forecast and Dispersion Outlook \\of Allegheny County, Pennsylvania for 2022-05-14}
\newcommand\AQIPittTodayColor{6AFE19}
\newcommand\AQIPittTomColor{FFF421}
\newcommand\AQILCTodayColor{6AFE19}
\newcommand\AQILCTomColor{FFF421}
\newcommand\AQIDateToday{05/14/2022}
\newcommand\AQIDateTom{05/15/2022}
\newcommand\AQIWeekToday{Saturday}
\newcommand\AQIWeekTom{Sunday}
\newcommand\inversionmode{observation}
